---
title: "Client Report (Placeholder)"
author: "Parham Pishrobat, Sarah Masri, Johnson Chen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup}
library(tidyverse)
library(lubridate)
library(rlang)
library(visdat)
source("../code/EDA.R")
source("../code/ITSA.R")
source("../code/GEE.R")
source("../code/LMEM.R")
```




## Introduction

   - Background of the study.
   - Objective(s) of the study.
   - Statistical questions to answer.

Concerns around sugar consumption and its health implications have prompted an array of interventions aimed at modifying consumer behaviours in relation to sugary beverages. The current study investigates the effectiveness of various strategies to encourage consumers to choose zero-calorie beverages over sugary alternatives. In particular, the research question focuses on the impact of two types of visual presentations of calorie content through posters that highlight either the calorie content or the physical activity required to burn these calories. Furthermore, the effectiveness of price discounts, both independently and in conjunction with explanatory messaging, as a means to influence consumer choices is explored. 

## Data Description and Summaries

   - Data collection method.
   - Study design.
   - Sample size.
   - Variables measured.
   - Missing data.

The data has been collected data from  cafeterias and convenience shops within three hospital sites, denoted by A, B, C, after conducting the interventions. Hospitals A is urban and has two cafeterias and two convenience shops. Hospital B is also urban setting and but has only one cafeteria. And finally hospital C is suburban setting, and has one cafeteria and one convenience shop. Both interventions (delivery of discount or the messaging type) and data collection  (recording the sales) was automatic at site A and by trained personnel in sites B and C. In the context of this study, sugary beverages include regular soft drinks and iced teas that are sweetened with natural sugars like sucrose and corn syrup, and zero-calorie beverages include diet soft drinks and teas, and water. Note that other beverage types like juices, milk, coffee, and fountain-dispensed drinks are excluded due to categorization challenges.

The study adopts an interrupted time-series multi-site quasi-experimental design to assess the outcomes of five distinct interventions on the purchase patterns of bottled sugary and zero-calorie beverages. The interventions consist of two price discounts and three calorie messaging strategies, each designed to influence consumer purchasing behaviour towards healthier beverage options. The price interventions involved a 10% discount on zero-calorie beverages, with one intervention additionally providing explanatory messaging about the discount. The calorie messaging interventions varied in their approach, providing information on the caloric content of sugary beverages, the physical activity required to burn off these calories, and a combination of both strategies.

The primary outcome of interest is daily sales of bottled sugary and zero-calorie beverages over a span of 30 weeks, from October 27 to May 23. The study periods include baseline data collection phases, intervention phases for both price discounts and calorie messaging, and washout periods to assess the persistence of intervention effects. 

(INCOMPLETE)

  

```{r data, include=FALSE}
beverage_sales <- read.csv("../rawdata/june1data.csv")[,1:6]
# head(beverage_sales)
# dim(beverage_sales)
```

```{r Summarize Data}
# summarize_data(beverage_sales)$numerical
# unique(beverage_sales$Site)
# unique(beverage_sales$Intervention)
```

## 3. Exploratory Analysis

NOTE: we will figure out the order and title of these sub sections at the end

### histogram and scatter plots, boxplot (Par; almost done)

```{r Plot Histograms}
plot_histograms(beverage_sales)
```


```{r Boxplots}
boxplots_by_category(beverage_sales, "Intervention")
```


```{r Scatter Plots}
scatter_plots(beverage_sales)
```

```{r Sales Scatterplot}
plot_beverage_sales_comparison(beverage_sales, "ZeroCal", "Sugary", "Site")
```

### correlation plot (Johnson)
   

```{r correlation}

```


### imbalance/missing value (Sarah)  visdat

```{r data quality}
plot_missing_data(beverage_sales, group_by_site=TRUE, group_by_intervention=FALSE)
plot_missing_data(beverage_sales, group_by_site=FALSE, group_by_intervention=TRUE)
```




### line plot for trajectory (Par)


```{r line plots}

```
   




## 4. Formal Analysis

```{r Handle Missing Data}
# handle_missing_data(beverage_sales)$MissingOverview
```

### ITSA (Par)

```{r itsa}

```



### GEE (Sarah)

```{r gee}

```


### LMEM (Johnson)

```{r lmem}

```
   

## 5. Conclusions
   
   - Recommendations to the clients.

## 6. References
   
   - Properly formatted citations.

## 7. Statistical Appendix
   
   - Mathematical formulas.
   - Additional tables/figures.






