---
title: "Client Report (Placeholder)"
author: "Parham Pishrobat, Sarah Masri, Johnson Chen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup}
library(tidyverse)
library(lubridate)
library(rlang)
library(visdat)
source("../code/EDA.R")
source("../code/ITSA.R")
source("../code/GEE.R")
source("../code/LMEM.R")
```




## Introduction

   - Background of the study.
   - Objective(s) of the study.
   - Statistical questions to answer.

Concerns around sugar consumption and its health implications have prompted an array of interventions aimed at modifying consumer behaviours in relation to sugary beverages. The current study investigates the effectiveness of various strategies to encourage consumers to choose zero-calorie beverages over sugary alternatives. In particular, the research question focuses on the impact of two types of visual presentations of calorie content through posters that highlight either the calorie content or the physical activity required to burn these calories. Furthermore, the effectiveness of price discounts, both independently and in conjunction with explanatory messaging, as a means to influence consumer choices is explored. 

## Data Description and Summaries

   - Data collection method.
   - Study design.
   - Sample size.
   - Variables measured.
   - Missing data.

The data has been collected data from  cafeterias and convenience shops within three hospital sites, denoted by A, B, C, after conducting the interventions. Hospitals A is urban and has two cafeterias and two convenience shops. Hospital B is also urban setting and but has only one cafeteria. And finally hospital C is suburban setting, and has one cafeteria and one convenience shop. Both interventions (delivery of discount or the messaging type) and data collection  (recording the sales) was automatic at site A and by trained personnel in sites B and C. In the context of this study, sugary beverages include regular soft drinks and iced teas that are sweetened with natural sugars like sucrose and corn syrup, and zero-calorie beverages include diet soft drinks and teas, and water. Note that other beverage types like juices, milk, coffee, and fountain-dispensed drinks are excluded due to categorization challenges.

The study adopts an interrupted time-series multi-site quasi-experimental design to assess the outcomes of five distinct interventions on the purchase patterns of bottled sugary and zero-calorie beverages. The interventions consist of two price discounts and three calorie messaging strategies, each designed to influence consumer purchasing behaviour towards healthier beverage options. The price interventions involved a 10% discount on zero-calorie beverages, with one intervention additionally providing explanatory messaging about the discount. The calorie messaging interventions varied in their approach, providing information on the caloric content of sugary beverages, the physical activity required to burn off these calories, and a combination of both strategies.

The primary outcome of interest is daily sales of bottled sugary and zero-calorie beverages over a span of 30 weeks, from October 27 to May 23. The study periods include baseline data collection phases, intervention phases for both price discounts and calorie messaging, and washout periods to assess the persistence of intervention effects. 

(INCOMPLETE)

  

```{r data, include=FALSE}
beverage_sales <- read.csv("../rawdata/june1data.csv")[,1:6]
# head(beverage_sales)
# dim(beverage_sales)
```

```{r Summarize Data}
# summarize_data(beverage_sales)$numerical
# unique(beverage_sales$Site)
# unique(beverage_sales$Intervention)
```

## 3. Exploratory Analysis

NOTE: we will figure out the order and title of these sub sections at the end

### histogram and scatter plots, boxplot (Par; almost done)

```{r Plot Histograms}
plot_histograms(beverage_sales)
```


```{r Boxplots}
boxplots_by_category(beverage_sales, "Intervention")
```


```{r Scatter Plots}
scatter_plots(beverage_sales)
```

```{r Sales Scatterplot}
plot_beverage_sales_comparison(beverage_sales, "ZeroCal", "Sugary", "Site")
```

### correlation plot (Johnson)
   

```{r correlation}

```


### imbalance/missing value (Sarah)  visdat

```{r data quality}
plot_missing_data(beverage_sales, group_by_site=TRUE, group_by_intervention=FALSE)
plot_missing_data(beverage_sales, group_by_site=FALSE, group_by_intervention=TRUE)
```




### line plot for trajectory (Par)


```{r line plots}

```
   




## 4. Formal Analysis

```{r Handle Missing Data}
# handle_missing_data(beverage_sales)$MissingOverview
```

### ITSA (Par)

```{r itsa}

```



### GEE (Sarah)

The Generalized Estimating Equations (GEE) approach is a convenient and relatively easy to interpret method to model longitudinal data. GEE is suitable for analyzing the data from this study since daily sales of bottled sugared beverages and zero-calorie beverages were measured repeatedly over time. GEE can be thought of as an extension of the Generalized Linear Model to longitudinal data (Columbia University). This method is particularly convenient due to its high statistical power, built-in handling of missing at random data, and its ability to account for within-subject correlation in non-normal data. 

Since the study aims to investigate the number of beverages sold at each site, this method assumes an outcome of zero-calorie and sugary beverages sold. Predictors include intervention type, site, day of the week, and total beverage sales. Site, day of the week, and total beverage sales predictors allow the model to adjust for any extraneous effects and possible sale or time trends independent of the studies interventions. Since this method models count data, a log link function is most appropriate, such as the Poisson or Negative Binomial. Models may be fitted over all sites simultaneously, or as one model per site. In the latter case, the sit factor may be excluded from the model. It is appropriate to try both to examine comparable results. Once the models are fitted, the GEE method will return coefficients for every intervention or combination of interventions taken during the study. These can be interpreted to help answer the studies main objectives. Namely, to examine how each intervention affected zero-calorie and sugary beverage sales, how sales differed by site, and comparing the impacts between different interventions on zero-calorie and sugary beverages sales. Hypothesis tests can be performed on each coefficient to test intervention and site effects. A Bonferroni correction is needed to adjust for increased risk of Type I error when making multiple statistical tests. 

```{r gee}

```


### LMEM (Johnson)

```{r lmem}

```
   

## 5. Conclusions
   
   - Recommendations to the clients.

## 6. References
   
   - Properly formatted citations.
   
   Columbia University Mailman School of Public Health. (n.d.). Repeated Measures Analysis. Columbia University Mailman School of Public Health. https://www.publichealth.columbia.edu/research/population-health-methods/repeated-measures-analysis

## 7. Statistical Appendix
   
   - Mathematical formulas.
   - Additional tables/figures.


### GEE Model

Let ${\bf Y_i}$ be the outcome variable for beverage $i$ (zero-calorie or sugared) sales.  

Let $g(\cdot)$ be the log link function (Poisson or Negative Binomial). Then, for design matrix ${\bf X}$ including all revenant predictors, the model can be written more explicitly as

\begin{align*}
g(\mathbb{E}[Y_i]) &= \beta_{0i} + \beta_{1i} (\text{Discount}) + \beta_{2i} (\text{Discount + Messaging}) + \beta_{3i} (\text{Calorie Messaging 1})  \\
&\hspace{3mm} + \beta_{4i} (\text{Calorie Messaging 2}) + \beta_{5i} (\text{Calorie Messaging 3}) + \beta_{6i} (\text{site B}) + \beta_{7i} (\text{site C})\\
&\hspace{3mm} + \beta_{8i} (\text{Day of Week})+ \beta_{9i} (\text{Total sales})
\end{align*}


Then $\beta_{0i}$ is the intercept. (Discount) and (Discount + Messaging) are each dummy variables to represent the discount intervention without messaging, and discount with messaging respectively. (Site B) and (Site C) are also dummy variables to indicate the site, with the baseline being site A.  





